Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-11 paper/main.tex
Changed supercop double sha256 to worst-case scenario

\section{\ac{SUPERCOP} results}
We see in tables \ref{tbl:supercop:long}, \ref{tbl:supercop:4096},
\ref{tbl:supercop:1536}, \ref{tbl:supercop:576}, \ref{tbl:supercop:64} and
\ref{tbl:supercop:8} that in general BLAKE, \ac{BMW}, Luffa, Shabal and Simd
outperform \ac{SHA}-256. However, given that Tahoe-LAFS uses double
\ac{SHA}-256, this means that it will also have to hash another 32 bytes for
every message it hashes. Since \ac{SUPERCOP} does not have benchmark for 32
byte messages, we will have to estimate the amount of cycles required for this.
If we assume that cycles/bytes is linear from 8 byte to 64 byte, we get the
following estimate for the speed of hashing 32 bytes:

$$179.62 - \frac{179.62 - 38.12}{64 - 8} * (32-8)= 118.98 (Cycles/byte)$$

We can then estimate the result of each message by the following formula:
$$\frac{median * size + 118.98*32}{size} = SHA256d estimate$$

\input{tables/supercop_sha256d}
Estimates based on this calculation are shown in Table
\ref{tbl:supercop:sha256d}. What we can see is that for lower lengths of data,
more of the candidates are faster than double \ac{SHA}-256. However, given the
practical situation that Tahoe-\ac{LAFS} is a file system, most files processed
will have be larger than the file sizes estimated here. Even though not all
hashing operations done in Tahoe are related to the file size, we expect that
only BLAKE, \ac{BMW}, Luffa, Shabal and SIMD will be able to outperform double
\ac{SHA}-256.

>>>>

\section{\ac{SUPERCOP} results}
We see in tables \ref{tbl:supercop:long}, \ref{tbl:supercop:4096},
\ref{tbl:supercop:1536}, \ref{tbl:supercop:576}, \ref{tbl:supercop:64} and
\ref{tbl:supercop:8} that in general BLAKE, \ac{BMW}, Luffa, Shabal and Simd
outperform \ac{SHA}-256. However, given that Tahoe-LAFS uses double
\ac{SHA}-256, this means that it will also have to hash another 32 bytes for
every message it hashes. Since \ac{SUPERCOP} does not have benchmark for 32
byte messages, we will have to estimate the amount of cycles required for this.
If we assume a worst case scenario of hashing 32 bytes, where the cycles/byte
count is exactly the same as for 8 bit median we get:

$$\frac{median * size + 179.62*32}{size} = SHA256d estimate$$

\input{tables/supercop_sha256d}
Estimates based on this calculation are shown in Table
\ref{tbl:supercop:sha256d}. What we can see is that for lower lengths of data,
more of the candidates are faster than double \ac{SHA}-256. However, given the
practical situation that Tahoe-\ac{LAFS} is a file system, most files processed
will be larger than the file sizes estimated here. Not all hashing
operations in Tahoe-\ac{LAFS} are strictly dependant on the original file size,
which would mean that all candidates would have a chance of outperforming
double \ac{SHA}-256. However this estimate is worst case, which leads us to the
belief that at least for larger input sizes (over 1536) only the five fastest
candidates will have a change of outperforming double \ac{SHA}-256.
